### 2017-12-18 manuscript.rmd
added model testing for median depth reconstruciton
added model testing for palpons

```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS
 plotTree(ultratree, lwd = 4)
 colors = c("black", "red")
 names(colors) = c("Absent", "Present")
 palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
 nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
 add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
palpons_obj <- densityMap(palpons_sim, plot=FALSE)
palpons_obj$cols[1:length(palpons_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(palpons_obj$cols))
 pdf("figures_raw/figure_5_raw_palpons.pdf")
 plot(palpons_obj)
 dev.off()
```

@@

>>>>

```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS

##MODEL test
fitDiscrete(ultratree, palpons, model="ER")$opt$aicc #24.85
fitDiscrete(ultratree, palpons, model="ARD")$opt$aicc #24.60

 plotTree(ultratree, lwd = 4)
 colors = c("black", "red")
 names(colors) = c("Absent", "Present")
 palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
 nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
 add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
palpons_obj <- densityMap(palpons_sim, plot=FALSE)
palpons_obj$cols[1:length(palpons_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(palpons_obj$cols))
 pdf("figures_raw/figure_5_raw_palpons.pdf")
 plot(palpons_obj)
 dev.off()
```

@@

fitContinuous(ultratree, median_extended, model="white")$opt$aicc
fitContinuous(ultratree, median_extended, model="BM")$opt$aicc
fitContinuous(ultratree, median_extended, model="OU")$opt$aicc
